It's Never Too Late To Learn\\ \emph{A case for ML in distributed systems}

### 2016-01-21 writeups/msr_workshop/paper.tex
microedits

Building a modern distributed service that guarantees service-level objectives
is hard. Complexity is introduced by the deployment environment and exacerbated
as the service evolves with time to accommodate hardware/environment changes or
support new features.
For example, to build a simple caching layer that guarantees a certain response
latency and throughput, developers need to take into account the number of
machines available to run that service, the network connecting these machines,
the storage hierarchy within each machine, and the expected workload that the
caching layer will be servicing. A change in any one of these parameters, could
render the service inefficient.

Traditionally, this complexity is addressed with custom-built systems that
are optimized for specific configurations and objective functions. Is there a
general, principled, approach to dealing with complexity in the design of
distributed systems?
In this position paper, we propose a research project to study the use of
Machine Learning (ML) in the design of distributed systems. We highlight
specific examples of where ML can help, and discuss potential issues that need
to be addressed.

@@

\subsection{Hierarchy}
Distributed systems are often designed in a hierarchical manner, where
subcomponents are monitoring and managing others. These components and layers of
indirection simplify reasoning about the system at large. However, it is not
clear how will hierarchy affect an ML agent.
\begin{itemize}
  \item Will hierarchy aid the learning system via parallelism? Or will it hinder
    it since not all features are visible at every level?
  \item Should learning happen in each component of the system? Or should it be
    centralized?
  \item If learning is happening at multiple levels of the hierarchy, will that
    create interference between the learners? Or will they compliment each
    other?
\end{itemize}

>>>>

Building a modern distributed service that guarantees service-level objectives
is hard. Complexity is introduced by the deployment environment and exacerbated
as the service evolves with time to accommodate hardware/environment changes or
support new features.
For example, to build a simple caching layer that guarantees a certain response
latency and throughput, developers need to take into account the number of
machines available to run that service, the network connecting these machines,
the storage hierarchy within each machine, the expected workload that the
caching layer will be servicing, and interference from other applications on the network and machines.
A change in any one of these parameters could render the service inefficient.

Traditionally, this complexity is addressed with custom-built systems that
are optimized for specific configurations and objective functions. Is there a
general, principled approach to dealing with complexity in the design of
distributed systems?
In this position paper, we propose a research project to study the use of
Machine Learning (ML) in the design of distributed systems. We highlight
specific examples of where ML can help, and discuss potential issues that need
to be addressed.

@@

\subsection{Hierarchy}
Distributed systems are often designed in a hierarchical manner, where
subcomponents are monitoring and managing others. These components and layers of
indirection simplify reasoning about the system at large. However, it is not
clear how hierarchy will affect an ML agent.
\begin{itemize}
  \item Will hierarchy aid the learning system via parallelism? Or will it hinder
    it since not all features are visible at every level?
  \item Should learning happen in each component of the system? Or should it be
    centralized?
  \item If learning is happening at multiple levels of the hierarchy, will that
    create interference between the learners? Or will they complement each
    other?
\end{itemize}
